### 2015-04-03 Workshop2015/current-version/incremental.tex
no message

\begin{trivlist}\sf\footnotesize
\item[~-~S$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$, agreedSLA$_i$.

                engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
\end{trivlist}

Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, the first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size. In other words, it will returns the cost of the data, as well as its actual size and location.

@@

ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy either user preferences and  service offering described through their \textit{Agreed SLAs}. Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the user preferences. For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week. Besides, she wishes her privacy be saved by adapting the anonymity process with regard to service reputation. The maximum total cost will condition also which kind of privacy preserving algorithms to apply.

\begin{trivlist}\sf\footnotesize
\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$. 
\end{trivlist}

@@

The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process that complies both the user cloud SLAs and QoS preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots.
 This allows computing a result as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} will be used to produce a \textit{derived SLA} to be associated to the query. These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results. The \textit{agreed SLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derived SLA} or a partial compliance that requires a negotiation step. For both alternatives, an \textit{integration SLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integration SLA}.

@@

@@

Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
In the case of our query example the following composition can be used for answering it:

\begin{footnotesize}
\sf
\begin{tabbing}
 -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
 \>  myLoc = loc(myIPaddress), \\
 \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
 \>  query total cost + cost $\leq$ \$1,\\
 \>  availability $\geq$ 90$\%$, \\
 \>  freshness = any, \\
 \>  provenance = ``expert'', \\
 \>  duration = 7 days, \\
 \>  I/0 volume/month $\leq$ 8GB, \\
 \>reputation level :] $\geq \lambda$ (the threshold) \\
 \>  storageSpace $\leq$ 1GB, \\
 \>  engage(``E.Dickinson'', size, myCreditCard).
 \end{tabbing} 
\end{footnotesize}

>>>>

\color{green}
\begin{trivlist}\sf\footnotesize
\item[~-~]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), 
%QoS preferences$_\mathit{user}$, -- These should be in the query... not in the concrete services specification.
agreedSLA$_i$.

\item[~-~]engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
\end{trivlist}

%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size. In other words, it will returns the cost of the data, as well as its actual size and location.

@@

ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy both user preferences and  service offering described through their \textit{Agreed SLAs}. 
Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the \textit{user preferences}, noted by {QoS preferences}$_\mathit{user}$:
\begin{trivlist}\sf\footnotesize
\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost, freshness, provenance, location, duration, privacy-preserving$\rangle$. 
\end{trivlist}

Let us suppose that for this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week. Besides, she wishes her privacy be saved by adapting the anonymity process with regard to service reputation. The maximum total cost will condition also which kind of privacy preserving algorithms to apply.

\begin{trivlist}\sf\footnotesize
\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$. 
\end{trivlist}

@@

\color{green}

The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process:
Given the user query, specified as a sequence of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
The algorithm in~\cite{CostaAMR13} is being modified to deal with SLA and QoS user preferences.

In this paper, we are interested in rewritten queries that comply with the user preferences,  cloud SLAs and QoS preferences.
 This allows computing a result as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} will be used to produce a \textit{derived SLA} to be associated to the query. These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results. The \textit{agreed SLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derived SLA} or a partial compliance that requires a negotiation step. For both alternatives, an \textit{integration SLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integration SLA}.

@@

\color{green}
Answer by Martin: The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process. Only those compositions that comply with the agreedSLA will be presented as solutions to the user.

@@

\color{green}
%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.

The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process. Only those compositions that comply with the agreedSLA will be presented as possible solutions to the user.
\color{black}

In the case of our query example the following composition can be used for answering it:

\begin{footnotesize}
\sf
\begin{tabbing}
 -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
 \>  myLoc = loc(myIPaddress), \\
 \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
 \>  query total cost + cost $\leq$ \$1,\\
 \>  availability $\geq$ 90$\%$, \\
 \>  freshness = any, \\
 \>  provenance = ``expert'', \\
 \>  duration = 7 days, \\
 \>  I/0 volume/month $\leq$ 8GB, \\
 \>  reputation level $\geq \lambda$ (the threshold) \\
 \>  storageSpace $\leq$ 1GB, \\
 \>  engage(``E.Dickinson'', size, myCreditCard).
 \end{tabbing} 
\end{footnotesize}
